---
title: "NormalityTest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NormalityTest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NormalityTest)
```

# Introduction
This vignette is aimed at showing you hints to use the functions that are part 
of the `NormalityTest` package.

# Datasets
This package comes with a specific dataset (see `?arrivals` for more info).

```{r arrivals.head, echo=TRUE}
head(arrivals,20)
```


Here below is the code that was used to generate it !

`set.seed(20200503)`   
`nData <- 1000`  
`arrivals <- data.frame( gender = rbinom(nData, size = 1, prob = 0.5),`    
`                        time = rpois(n = nData, lambda = 3),`  
`                        weight = rnorm(n = nData, mean = 60, sd = 5),`     
`                        age = rnorm(n = nData, mean = 35, sd = 10) )`      
`arrivals$weight <- arrivals$weight + 20*arrivals$gender`   
`arrivals$gender <- factor(arrivals$gender)`   
`levels(arrivals$gender) <- c("female", "male")`  


# Example

Testing the `normality.df` function on the `arrivals`data :

```{r example, echo=TRUE, fig.height = 4, fig.width = 6}
tst <- normality.df(arrivals, output = "figure")
```


